Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-03-16 journal-draft/bare_jrnl_comsoc.tex
notation for secondary users

As to a pair of secondary users, when the Euclidean distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other. DEFINE DISTANCE! \textcolor{brown}{distance, done}
%
If a secondary user $n$ is not in the transmission range of a primary user $u$, $n$ can certainly not detect the presence of $u$.
As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in \mathcal{N}$, $C_n = C_{n'}$ does not necessarily hold.	
%
%Neighbourhood establishment and maintenance with control channel and according to a neighborhood discovery protocol which is out of scope of our work.
%While primary users are assumed to be fixed, secondary users can be mobile.
%Validation refers to the process of ensuring that no primary transmission is actually taking place on the respective channel.
%All $N$ secondary users constitute an ad-hoc network in which data can be transmitted from one certain node to any other node should available c.hannels are available on the source node, destination node and other intermediate nodes.
%Communication on licensed channels is possible only when nodes $i, j$ are both located in each other's transmission range and both share a validated licensed channel.
As the assumed $0/1$ state \textcolor{red}{(What is that?? Define! Fix it TODO)}\textcolor{brown}{Di: 0/1 means the connectivity is either available or not} of connectivity is solely based on the Euclidean distance between secondary users,
%CRN can be represented by a graph $\mathcal{G}(I,\mathcal{E})$, where $\mathcal{E}=\lbrace(i,j,v) \vert i, j \in \mathcal{N} \wedge v\in V_i \wedge v\in V_j \rbrace$ is wireless link between any secondary node $i$ and its neighbour $j$ with licensed channel $v$.
%Due to relatively low primary user dynamics, time index is omitted here.
%%In order to perform clustering, CR users first need to establish their neighborhood.
%For secondary node $i$, its neighborhood $Nb_i$ consists of all the secondary users locating within its transmission range, regardless whether common licensed channels exist or not. 
%% and have at least one common channel with node $i$ each, i.e. $ j\in Nb_i \Rightarrow V_i\cap V_j\neq \emptyset$.
%%The clustering phase is initialized during which any control message is again conveyed by the control channel.
%In the rest of this paper, \textit{channel} only refers to the licensed common control channel unless the dedicated control channel is particularly mentioned.

A cognitive radio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$. Note that we consider the channel availability only for \textit{one} snapshot of time. For the rest of this paper the word channel is referred to licensed channel, if the control channel is not explicitly mentioned.

\subsection{Clustering}
\label{def_cluster}
%We give the description of cluster in the context of CRN, all the clusters discussed in this paper comply with it.
%A cluster $C$ is composed with one cluster head and cluster members, which satisfies the following conditions:
%\begin{itemize}
%\item Cluster head $H_C$ is able to communicate with any cluster member \textit{directly}, \ie for any cluster member $i\in C$, there is $i\in \texttt{Nb}_{H_C}$.
%\item There exists as least one common control channel in the cluster, \ie $\cap_{i\in C} V_i \neq \emptyset$.
%\end{itemize}
In this section, we describe what a cluster in the context of CRNs means. A cluster $\textsf{Cl} \subseteq \mathcal{N}$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{Cl}}$ and a number of cluster members. The cluster head is able to communicate with any cluster member directly. In other terms, for any cluster member $m \in \textsf{Cl}$, $m \in N \left( h_{\textsf{Cl}} \right)$ holds.

@@

\begin{table}[h!]
\caption{Notations in robust clustering problem}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{P}$, $\mathcal{N}$  & collection of primary and secondary users\\
$P$, $N$ & the number of primary users and secondary users\\
%$J$ & set of primary uesrs in the scenario\\
$\mathcal{F}$ & set of non-overlapping channels in the scenario\\
$\texttt{Nb}_i$ & node $i$' neighborhood     \\
$C$ & a cluster \\
$C_i$ & a cluster whose cluster head is $i$ \\
& (in Section~\ref{centralized_scheme}, $C_i$ is the $i$th cluster \\
& among the legitimate clusters.)\\
$V_i$   & set of available channels at CR node $i$  \\
$V_C$   & set of available CCCs of cluster $C$  \\
$V_{C_i}$   & set of available CCCs of cluster $C_i$\\
%$\phi_i$ & the number of available channels for cluster $i$\\ 
%		& note it is different than $|V_i|$\\
%$p_i$   & number of available channels on CR node $i$  \\
$H_C$ & cluster head of a cluster $C$\\
$\delta$ & desired cluster size\\
%$C_i$ & a cluster with CR node $i$ as cluster head \\
%$V_{C_i}$   & set of common channels within cluster $C_i$  \\
%$V_{OC_i}$   & set of common channels among cluster $C_i$ and neighbor clusters  \\
%$CH_i$ & cluster head of node $i$ \\
%$CHS_i$ & set of cluster heads of node $i$ after phase I\\
$S_i$ & set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
$K_{C_i}$ & set of CCCs within cluster $C_i$\\
$k_{C_i}$ & num. of CCCs of cluster $C_i$, $k_{C_i} = |K_{C_i}|$\\
%$m_{ij}$ & number of common channels between CR node \\
%& $i$ and $j$\\
\bottomrule
\end{tabular}
\end{table}

>>>>

As to a pair of secondary users, when the Euclidean distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other. DEFINE DISTANCE! \textcolor{brown}{distance, done}
%
If a secondary user $n$ is not in the transmission range of a primary user $u$, $n$ can certainly not detect the presence of $u$.
As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in V_N$, $C_n = C_{n'}$ does not necessarily hold.	
%
%Neighbourhood establishment and maintenance with control channel and according to a neighborhood discovery protocol which is out of scope of our work.
%While primary users are assumed to be fixed, secondary users can be mobile.
%Validation refers to the process of ensuring that no primary transmission is actually taking place on the respective channel.
%All $N$ secondary users constitute an ad-hoc network in which data can be transmitted from one certain node to any other node should available c.hannels are available on the source node, destination node and other intermediate nodes.
%Communication on licensed channels is possible only when nodes $i, j$ are both located in each other's transmission range and both share a validated licensed channel.
As the assumed $0/1$ state \textcolor{red}{(What is that?? Define! Fix it TODO)}\textcolor{brown}{Di: 0/1 means the connectivity is either available or not} of connectivity is solely based on the Euclidean distance between secondary users,
%CRN can be represented by a graph $\mathcal{G}(I,\mathcal{E})$, where $\mathcal{E}=\lbrace(i,j,v) \vert i, j \in \mathcal{N} \wedge v\in V_i \wedge v\in V_j \rbrace$ is wireless link between any secondary node $i$ and its neighbour $j$ with licensed channel $v$.
%Due to relatively low primary user dynamics, time index is omitted here.
%%In order to perform clustering, CR users first need to establish their neighborhood.
%For secondary node $i$, its neighborhood $Nb_i$ consists of all the secondary users locating within its transmission range, regardless whether common licensed channels exist or not. 
%% and have at least one common channel with node $i$ each, i.e. $ j\in Nb_i \Rightarrow V_i\cap V_j\neq \emptyset$.
%%The clustering phase is initialized during which any control message is again conveyed by the control channel.
%In the rest of this paper, \textit{channel} only refers to the licensed common control channel unless the dedicated control channel is particularly mentioned.

A cognitive radio network (CRN) can be represented as an undirected graph $G = (V_N, E)$, where $E \subseteq V_N \times V_N$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$. Note that we consider the channel availability only for \textit{one} snapshot of time. For the rest of this paper the word channel is referred to licensed channel, if the control channel is not explicitly mentioned.

\subsection{Clustering}
\label{def_cluster}
%We give the description of cluster in the context of CRN, all the clusters discussed in this paper comply with it.
%A cluster $C$ is composed with one cluster head and cluster members, which satisfies the following conditions:
%\begin{itemize}
%\item Cluster head $H_C$ is able to communicate with any cluster member \textit{directly}, \ie for any cluster member $i\in C$, there is $i\in \texttt{Nb}_{H_C}$.
%\item There exists as least one common control channel in the cluster, \ie $\cap_{i\in C} V_i \neq \emptyset$.
%\end{itemize}
In this section, we describe what a cluster in the context of CRNs means. A cluster $\textsf{Cl} \subseteq V_N$ is a set of secondary nodes consisting of a cluster head $h_{\textsf{Cl}}$ and a number of cluster members. The cluster head is able to communicate with any cluster member directly. In other terms, for any cluster member $m \in \textsf{Cl}$, $m \in N \left( h_{\textsf{Cl}} \right)$ holds.

@@

\begin{table}[h!]
\caption{Notations in robust clustering problem}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{P}$, $\mathcal{N}$  & collection of primary and secondary users\\
$\mathcal{F}$ & set of non-overlapping channels in the scenario\\
$N(n)$ & neighborhood of node $n$    \\
$C$ & a cluster -- remove ? \\
$C_i$ & a cluster whose cluster head is $i$ -- remove ? \\
& (in Section~\ref{centralized_scheme}, $C_i$ is the $i$th cluster \\
& among the legitimate clusters.) -- remove ?\\
$V_i$   & set of available channels at CR node $i$ --$V$ is usually a set of vertices \\
$V_C$   & set of available CCCs of cluster $C$ --$V$ is usually a set of vertices \\
$V_{C_i}$   & set of available CCCs of cluster $C_i$ --$V$ is usually a set of vertices\\
%$\phi_i$ & the number of available channels for cluster $i$\\ 
%		& note it is different than $|V_i|$\\
%$p_i$   & number of available channels on CR node $i$  \\
$H_C$ & cluster head of a cluster $C$\\
$\delta$ & desired cluster size\\
%$C_i$ & a cluster with CR node $i$ as cluster head \\
%$V_{C_i}$   & set of common channels within cluster $C_i$  \\
%$V_{OC_i}$   & set of common channels among cluster $C_i$ and neighbor clusters  \\
%$CH_i$ & cluster head of node $i$ \\
%$CHS_i$ & set of cluster heads of node $i$ after phase I\\
$S_i$ & set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
$K_{C_i}$ & set of CCCs within cluster $C_i$\\
$k_{C_i}$ & num. of CCCs of cluster $C_i$, $k_{C_i} = |K_{C_i}|$\\
%$m_{ij}$ & number of common channels between CR node \\
%& $i$ and $j$\\
\bottomrule
\end{tabular}
\end{table}

\textcolor{red}{The notation is not well chosen. Does it make sense to have only one letter for a potential cluster? What happens if we have two clusters? Find some comments next to your proposed notation.}
